---
title: "Covid91 vaccine study Final2020"
author: "Flora Soto"
date: "October 22, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)  
#record aids to say covid and then remove the annoying "x" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK")) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.  

$H_0$: The Null Hypothesis is that among the target population there is no relation between the vaccine has no effect on whether one contacts the virus or not .  

$H_A$: The Alternative Hypothesis among the target population there is no relation between the vaccine has no effect on whether one contacts the virus or not.  


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->  

Every question is of a CAT ~CAT type

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->  

##Graphical Descriptive Results


```{r}  
DataF = filter(OldData,sex=="gal")
barchartGC(~infected + treatment, data= DataF)
barchartGC(~infected + treatment, data=DataF, type="percent",main="gals")  

```

##Graphical Descriptive Results

Among females that contracted Aids twice as many took the placebo. Therefore it appears that the vaccine does have a positive effect.  

```{r}  
DataG = filter(OldData,sex=="guy")
barchartGC(~infected + treatment, data= DataG)
barchartGC(~infected + treatment, data=DataG, type="percent",main="guys")  

```
Its appears that the vaccine has a negative effect on the guys since they are more likely to get COVID19 if have the vaccine  

##Graphical Descriptive Results  

```{r}  
DataGBTQ = filter(OldData,LGBTQ=="gay")
barchartGC(~infected + treatment, data= DataGBTQ)
barchartGC(~infected + treatment, data=DataGBTQ,type="percent",main="gays")  

```  
Its appears that the vaccine has a positive effect on the LGBTQ. There for it appears theres a positive affect.  
  
```{r}  
DataU = filter(FinalData,DrugUser=="yes")
barchartGC(~infected + treatment, data= DataU)
barchartGC(~infected+ treatment, data=DataU, type="percent",main="yes")  

``` 
  
###Numerical Summaries  
```{r}
table1 <- xtabs(~infected + treatment, data= DataF)
rowPerc(table1)
colPerc(table1)
```
###Numerical Summaries  
```{r}
table1 <- xtabs(~infected + treatment, data= DataG)
rowPerc(table1)
colPerc(table1)
```
##Numerical Summaries  
```{r}
table1 <- xtabs(~infected + treatment, data= DataGBTQ)
rowPerc(table1)
colPerc(table1)  
``` 
##Numerical Summeries
```{r}
table1 <- xtabs(~infected + treatment, data= DataU)
rowPerc(table1)
colPerc(table1)
```


##Inferential  

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
The fisher test shows the odds of getting COVID-19 are 0.55 to 1. The confidence intervals for the odd ratio is 0.36 to 0.82. 
# Discussion and Conclusion  

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->  

The female charts and numerical results the females that took the drug are less likely to contratc COVIC-19, on the women who took the drug only 33.11 got infected with COVID-19 and 50.31 where ok with the drug. in the interferential test that was 95.56% that were not infected making the vaccine effective among females. The p. value <2.2e-16, we fail to reject the null Hypothesis the vacicne did have an effect in te females whether they contracted COVID-19.

Male charts and numerical results males that took the vaccine were contracted COVID-19, 58.16 of the males who took treatment contracted covid and only 45.54 were ok. Data it seems that the men are most likely to contract covid-19 when given the vaccine. P.Value was of 6e-<0.05. We reject the null hypothesis the vaccine had no effect.

The LGBTQ data and numerical results 70.69 contract covid-19 with the treatment and only 49.17 did not contract the virus with the vaccine. this data it seems that the vaccine had no positive effect in the LGBTQ community and the community was still contracting the virus. P.Value was 1.05e-05which is less than 0.05 we reject the null hypothesis. the vaccine had no effect with the LGBTQ contracted covid-19.

The data from the drug users 33.33 contracted covid-19 with the treatment and 47.83 did not contract the virus with the treatment. the drugusers data we came closer to having the same results from people infected and people who had covid-19. looking at the p.value of the chi square we can now determine the effect of the vaccine. the p.value is 0.02273 .0.05 then we reject the null hypothesis and we can say that the vaccine did have an effect in the drugusers contracted covid-19.


